Notes on area-length problem for CLE

### 2014-04-17 CFT/area-length/notes.tex
Log update + Some text on flat surfaces

>>>>

\section{Liouville theory for flat surfaces}
\label{sec:liouv-theory-flat}

Now we will introduce Liouville theory for flat surfaces. We want to study closed loops in complex
plane. The interior of such a loop can be mapped to unit disk or upper half-plane. Since the loops
are on a flat plane and disk is in complex plane too we do not need to consider metrics with
non-zero curvature. But curvature on the boundary is non-zero. So we write the action in terms of
flat background metric $\hat g_{\mu\nu}$ with $\hat R=0$, but we on the boundary curvature $\hat
K\neq 0$.

We assume background-independence in the following sense. If $\hat g$ is flat metric then
$e^{\sigma}\hat g$ is also flat if $\Delta\sigma=0$ inside the domain $\mathcal{M}$. On the boundary
$\sigma$ is $2\pi$-periodic function. (The space of functions ${\varphi}$ is Hardy space).

Since the connection of parameters $b$, $Q$ and asymptotic of the fields $\chi, \varphi$ at infinity
for the theory on the upper half-plane is established from background-independence, we do not yet
know if $Q=b+\frac{1}{b}$. Also the choice of area and length terms $e^{2b\varphi}$ and
$e^{b\varphi}$ is not fixed,  even in usual Liouville theory it is possible to write boundary length
as $e^{\frac{\varphi}{b}}$ for fractal boundary with fractal dimension $2b^{2}$. So in our action we
leave parameters $b,a,Q$ free:
\begin{multline}
\label{eq:181}
  S[\chi,\varphi]=\int_{\mathcal{M}}\left(\frac{1}{4\pi}[(\nabla \varphi)^{2}+(\nabla
    \chi)^{2}]+\mu e^{2b\varphi}\right)d^{2}z +\\
  +  \int_{\partial
    \mathcal{M}}\left(\frac{1}{2\pi}(Q\varphi-ie_{0}\chi)\hat K + \mu_{B}e^{a\varphi}\right)dx+\mbox{ghosts}
\end{multline}
Let $\mathcal{M}=\mathbb{D}$ and $g_{\mu\nu}=\delta_{\mu\nu}$. Then the action is
\begin{equation}
  \label{eq:182}
   S[\chi,\varphi]=\int_{\mathbb{D}}\left(\frac{1}{4\pi}[(\nabla \varphi)^{2}+(\nabla
    \chi)^{2}]+\mu e^{2b\varphi}\right)d^{2}z +
    \int_{S^{1}} \left(\frac{1}{2\pi}(Q\varphi-ie_{0}\chi) + \mu_{B}e^{a\varphi}\right)dx+\mbox{ghosts}
\end{equation}
Let us change background metric to $\tilde g_{\mu\nu}=e^{\sigma}g_{\mu\nu}$, then the action is
\begin{equation}
  \label{eq:183}
  S_{\tilde g}[\chi,\varphi]=\int_{\mathbb{D}} \left( \frac{1}{4\pi} e^{2\sigma}\left[ (\nabla
      \varphi)^{2}+(\nabla \chi)^{2}\right] +\mu e^{2b\varphi}\right)d^{2}z +\int_{S^{1}} \left( \frac{1}{2\pi}
\end{equation}
